Effect of Election on Currency Fluctuation

### 2024-04-14 paper/paper.qmd
fixed rendering issues and changed directory for datasheet

### Construction of Inauguration Week

@@

## Explaination for small R^2
```{r}
colors <- c("No Inauguration Announcement" = "yellow", "Inauguration Announcement" = "blue")

>>>>

### Construction of Inauguration Week
$$Day1 \hspace{5mm} Day2 \hspace{5mm}  Day3 \hspace{7mm}  Inauguration\ Day \hspace{7mm} Day5 \hspace{5mm} Day6 \hspace{5mm} Day7$$

@@

## Explaination for small R^2
```{r}
#| label: fig-size_visual
#| fig-cap: Estimate average change in Exchange Rate
#| echo: false
#| warning: false
#| message: false
colors <- c("No Inauguration Announcement" = "yellow", "Inauguration Announcement" = "blue")
